Tools for Identifying Partisan Gerrymandering (PA)

### 2019-06-13 Latex/_maintext.tex
tex updates

    In addition to the rejected 2011 and the court-ordered 2018 map, we also address the partisan and other traditional features of two maps offered to the Pennsylvania Court as a proposed remedy for constitutional violation found in the 2011 map: the \textit{joint legislative} plan offered by Republican legislators from both chambers, and the congressional map proposed by the Democratic governor (\textit{Gov. Wolf}). Here we focus on the question of whether either of these plans was a \textit{stealth gerrymander} done to aid the party drawing the map.

@@

    As noted above, to contrast the Court-ordered Remedial plan with the 2011 Enacted plan, and to make further comparisons to the two most politically important remedy plans offered to the Court, the joint plan proposed by the Republicans leaders of the two legislative chambers, and the Governor’s proposed plan as a Democratic alternative, we will look at a number of features of each of these four plans as a whole.  We do not, however, discuss district-specific criteria for identifying gerrymandering in these maps, since, although some district-specific evidence was presented about the 2011 map in the trial testimony by an expert who was highly knowledgeable about communities of interest in the state, the Pennsylvania Supreme Court opinion itself offers a \underline{statewide} standard for a finding of unconstitutional partisan gerrymandering. 

@@

        \begin{center} INSERT TABLE \ref{tab:summaries} ABOUT HERE \end{center}
    We begin our analyses describing map features distinct from projected (or actual) partisan outcomes or proposed measures of partisan effects. Table \ref{tab:summaries} offers a comparison of two key good government features of the map.

@@

>>>>

    In addition to the rejected 2011 and the court-ordered 2018 map, we also address the partisan and other traditional features of two maps offered to the Pennsylvania Court as a proposed remedy for constitutional violation found in the 2011 map: the \textit{Joint Legislative} plan offered by Republican legislators from both chambers, and the map proposed by the Democratic governor (\textit{Gov. Wolf}). Here we focus on the question of whether either of these plans was a \textit{stealth gerrymander} done to aid the party drawing the map.

@@

    To facilatate comparisons to the two most politically important remedy plans offered to the Court, the joint plan proposed by the Republicans leaders of the two legislative chambers, and the Governor’s proposed plan as a Democratic alternative, we look at a number of features in each of the four plans as a whole. We do not, however, discuss district-specific criteria for identifying gerrymandering in these maps, since, although some district-specific evidence was presented about the 2011 map in the trial testimony by an expert who was highly knowledgeable about communities of interest in the state, the Pennsylvania Supreme Court opinion itself offers a \underline{statewide} standard for a finding of unconstitutional partisan gerrymandering. 

@@

@@

		\begin{center}\textbf{INSERT TABLE \ref{tab:summaries} ABOUT HERE} \end{center}
    We begin our analyses describing map features distinct from partisan outcomes or proposed measures of partisan asymmetries. Table \ref{tab:summaries} offers a comparison of two key good government features of the map.
